Notes and approaches to OCR

### 2020-12-08 outputs/documents/paper.Rmd
Reorganize directory and begin updating paper

---
title: "Notes and approaches to OCR"
author: "Rohan Alexander, John Tang, Diego Mamanche Castellanos"
date: "08 August 2020"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
---

@@

A crucial aspect of the data science workflow is gathering data. It involves the tools and methods used to collect information in an established systematic fashion and identify the variables being measured. It also describes the methods used to obtain the data. Although the data collection component of research remains the same regardless of the field of study, the methods used vary among those fields of study as they have different interests. Moreover, the diversity of data types adds complexity to the process of gathering data. Structured data is organized in a highly regular manner or a pre-defined data model where the regularities apply to all the data in a particular dataset. Some examples are tables and relations. Semi-structured data contains this same information, but instead of having regular structures applied to all items in the dataset, the data might be interpreted with structural information. It can be supplied as tags e.g. name = "Bob" but also other markers to separate semantic elements and enforce hierarchies of records and fields within the data. Finally, Unstructured data, such as texts or images, holds information with no explicit structured data, such as tags. However, these tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data $(Robert M. Losee, 2005)^1$. This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.

The Portable Document Format (PDF) is an example of unstructured data created by the company Adobe in the 90s. It is widely used for documents. According to the $ISO 32000-2:2017^2$, the latest edition of the PDF Reference (2.0), PDF enables users to exchange and view electronic documents easily and reliably, independent of the environment in which they were created or the environment in which they are viewed or printed. It is intended to fulfill the following requirements:

- preservation of document fidelity independent of the device, platform, and software,
- merging of content from diverse sources — Web sites, word processing and spreadsheet
programs, scanned documents, photos, and graphics — into one self-contained document while
maintaining the integrity of all original source documents,
- an extensible metadata model at the document and object level,
- collaborative editing of documents from multiple locations or platforms,
- digital signatures to certify authenticity,
- security and permissions to allow the creator to retain control of the document and associated
rights,
- accessibility of content to those with disabilities,
- extraction and reuse of content for use with other file formats and applications, and
- electronic forms to gather and/or represent data within business systems.

To mention some of the features incorporated in this version we have:

- 12.10, "Geospatial features";
- 13.7, "Rich media" annotations;
- 14.7.4, "Namespaces" for tagged PDF;
- 14.9.6, "Pronunciation hints";
- 14.12, "Document parts";
- 14.13, "Associated files";
- Support for PRC (see 13.6, "3D Artwork");
- Support for UTF-8.

However, these advantages mean that the data in PDFs cannot be used for quantitative statistical analysis. The reason is that it needs measurable and verifiable data. But PDF documents, as it was mentioned previously, can have different objects, some of them non-static objects compressed in the same document. This situation makes it difficult to extract valuable information from the paper.

Sometimes just by copying and pasting the information directly from the PDF is possible when it contains simple texts or regular tables. In that case, there is no barrier in the process of extracting data. But other times it is not as easy if it is an image, a survey form, or complex shapes containing relevant information. Furthermore, there is a linguistic component that adds more complexity. For instance, it is well known that non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process. It is because those characters have complicated structures, a huge number of categories, and resemblance among characters, font unevenness, or writing styles. In those cases, the need for reliable tools or methods with the ability to elicit data becomes extremely important.

Optical character recognition (OCR), a process that transforms a bitmapped image of printed or handwritten text into text code, and thereby making it machine-readable, has been widely used for scientists trying to capture the images of characters and texts back in the 50s. First, by mechanical and optical means of rotating disks and photomultiplier flying spot scanner with a cathode ray tube lens, followed by photocells and arrays of them. The OCR process was slow, and one line of characters could be digitized at a time. Nowadays, in OCR, once a printed or handwritten text has been captured optically by a scanner or some other optical means, the digital image goes through the following stages of a computer recognition system $(Cheriet, Mohamed; Kharma, 2007)^3$:

@@

@@

For the purpose of this study, one page from the letter a in the Japanese dictionary was taken to assess the selected OCR tools. The image contains 3293 characters. Words in English were counted as one character for this analysis. MOreover, the sample text was divided into four images called **sections** as it is illustrated in figure XX. These new images were assessed across all OCR tools.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/sections.png)
**Figure XX**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped%20pages/00-sample_pages_3_sec_1.png)
**Figure XX Section 1**

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped pages/00-sample_pages_3_sec_2.png)
**Figure XX Section 2**

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped pages/00-sample_pages_3_sec_3.png)
**Figure XX Section 3**

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped pages/00-sample_pages_3_sec_4.png)
**Figure XX Section 4**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/section1.png)
**Figure xx**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/region-section1.png)
 **Figure xx**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/lines-section1.png)   
 **Figure xx**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/boundaries-section1.png)
 **Figure xx**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/characters-section1.png)
 **Figure xx**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/self-detection.png)
 **Figure xx**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/japanese-parameter.png)
 **Figure 7**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/sections.png)
 **Figure xx**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/boundaries.png)
**Figure xx**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/characters.png)

**Figure xx**

@@

To use this library, we need to install Tesseract. For this study, we use version 4. IT is necessary to call the .exe file to use Tesseract with PyTesseract. See the following example.

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure11.png)
**Figure xx**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/page.png)
**Figure 12**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/blocks.png)
**Figure 13**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/paragraphs.png)
**Figure xx**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/lines.png)   
 **Figure xx**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/boundaries.png)   
 **Figure xx**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/characters.png)   
 **Figure xx**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/kindai-images/xml-processed.png)   
 **Figure XX**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/kindai-images/kindai-section1.jpg)
**Figure XX**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure18.png)   
 **Figure xx**

>>>>

---
title: "Notes and approaches to OCR"
author: "Rohan Alexander, John Tang, Diego Mamanche Castellanos"
date: "8 December 2020"
abstract: "TBD"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
bibliography: references.bib
---

@@

A crucial step in the data analysis workflow is gathering data. This step involves tools and methods to collect raw data in an systematic way. In this paper we are interested in gathering data from Portable Document Format (PDF) files, in particular, when these PDFs were created by scans, and hence must be processed before their data can be analysed. Such PDF files are unstructured data, meaning that the data are not tagged and are not organised in a regular way.^[Structured data is organized in a highly regular manner or a pre-defined data model where the regularities apply to all the data in a particular dataset. Some examples are tables and relations. Semi-structured data contains this same information, but instead of having regular structures applied to all items in the dataset, the data might be interpreted with structural information. It can be supplied as tags e.g. name = "Bob" but also other markers to separate semantic elements and enforce hierarchies of records and fields within the data. Unstructured data, such as texts or images, holds information with no explicit structured data, such as tags. However, these tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data [@Losee2006]. This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.] While tags could be assigned manually, typically a statistical model is used for reasons of efficiency, and this process is called Optical Character Recognition (OCR). We evaluate several pre-trained commercial OCR options accessed via APIs: 1) X, 2), and 3), ; additionally several OCR options that are run locally: 4) X, 5), and 6), ; and finally 7) training our own model. We find... **[TBD]**.

PDF files were developed in 1993 by the technology company Adobe and are useful for documents because they should display in a consistent way independent of the environment that created them or the environment in which they are being viewed. One feature of PDFs is that they can include a variety of objects, for instance, text, photos, figures, etc. However, this variety can limit the capacity of PDFs to be used directly as data inputs for statistical analysis. The data first needs to be extracted from the PDF.

Sometimes it is possible to copy and paste the data from the PDF. This is more likely when the PDF only contains simple text or regular tables. In particular, if the PDF has been created by an application such as Word then often the text can be extracted in this way because they are stored as text. But it is not as easy if the text has been stored as an image which is then part of the PDF

Furthermore, there is a linguistic component that adds more complexity. For instance, it is well known that non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process **[ADD CITE]**. It is because those characters have complicated structures, a large number of categories (for instance, compare the 26 characters in the English alphabet with the thousands of characters in Japanese kanji), and resemblance among characters, font unevenness, or writing styles. In those cases, the need for reliable tools or methods with the ability to elicit data becomes extremely important.

Optical character recognition (OCR),is a process that transforms a bitmapped image of printed or handwritten text into text code **[ADD CITE]**. It thereby becomes machine-readable. It has been used to parse images of characters since the 1950s **[ADD CITE]**. These initial approaches used mechanical and optical means of rotating disks and photomultiplier flying spot scanner with a cathode ray tube lens, followed by photocells and arrays of them **[ADD CITE]**. The OCR process was slow, and one line of characters could be digitized at a time. These days once a printed or handwritten text has been captured optically by a scanner or some other optical means, the digital image goes through the following stages of a computer recognition system [@Cheriet2007]:

@@

Although this step remains the same regardless of the field of study, the methods used vary between those fields of study because of their different interests. Moreover, the diversity of data types adds complexity to the process of gathering data.

@@

For the purpose of this study, one page from the letter a in the Japanese dictionary was taken to assess the selected OCR tools. The image contains 3293 characters. Words in English were counted as one character for this analysis. MOreover, the sample text was divided into four images called **sections** as illustrated in Figure \@ref(fig:sections). These new images were assessed across all OCR tools.

```{r sections, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/sections.png"))
```

@@

```{r section1, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("inputs/cropped_pages/00-sample_pages_3_sec_1.png"))
```

```{r section2, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("inputs/cropped_pages/00-sample_pages_3_sec_2.png"))
```

```{r section3, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("inputs/cropped_pages/00-sample_pages_3_sec_3.png"))
```

```{r section4, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("inputs/cropped_pages/00-sample_pages_3_sec_4.png"))
```

@@

```{r azuresection1, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/azure-images/section1.png"))
```

@@

```{r azureregionsection1, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/azure-images/region-section1.png"))
```

@@

```{r azureregionsection2, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/azure-images/lines-section1.png"))
```

@@

```{r azureregionsection3, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/azure-images/boundaries-section1.png"))
```

@@

```{r azureregionsection4, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/azure-images/characters-section1.png"))
```

@@

```{r azureregionsection5, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/azure-images/self-detection.png"))
```

@@

```{r azureregionsection6, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/azure-images/japanese-parameter.png"))
```

@@

```{r azureregionsection7, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/google-images/sections.png"))
```

@@

```{r azureregionsection8, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/google-images/boundaries.png"))
```

@@

```{r azureregionsection9, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/google-images/characters.png"))
```

@@

To use this library, we need to install Tesseract. For this study, we use version 4. It is necessary to call the .exe file to use Tesseract with PyTesseract. See the following example.

@@

```{r azureregionsectio98, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/figure11.png"))
```

@@

```{r azureregionsectio12, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/pytesseract-images/page.png"))
```

@@

```{r azureregionsectio13, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/pytesseract-images/blocks.png"))
```

@@

```{r azureregionsectio14, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/pytesseract-images/paragraphs.png"))
```

@@

```{r azureregionsectio15, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/pytesseract-images/lines.png"))
```

@@

```{r azureregionsectio16, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/pytesseract-images/boundaries.png"))
```

@@

```{r azureregionsectio17, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/pytesseract-images/characters.png"))
```

@@

```{r azureregionsectio27, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/kindai-images/xml-processed.png"))
```

@@

```{r azureregionsectio47, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/kindai-images/kindai-section1.jpg"))
```

@@

```{r azureregionsectio18, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
knitr::include_graphics(here::here("outputs/documents/figure18.png"))
```
